Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Section 6: Technical report titles do not need first letter capital.

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Exploring Sustainability group are:
\begin{itemize}
\item Mario Rosado de Souza, Robert Haines, and Caroline Jay. Defining
Sustainability through Developers' Eyes: Recommendations from an Interview
Study~\cite{wssspe2_rosada_de_souza}

\item Robert Downs, W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and
Nicholas Weber. Community Recommendations for Sustainable Scientific
Software~\cite{wssspe2_downs}

\item Abani Patra, Matthew Jones, Steven Gallo, Kyle Marcus, and Tevfik Kosar.
Role of Online Platforms, Communications and Workflows in Developing Sustainable
Software for Science Communities~\cite{wssspe2_patra}

\item Marlon Pierce, Suresh Marru, and Chris Mattmann. {WSSSPE2}: Patching It Up,
Pulling It Forward~\cite{wssspe2_pierce}

\item Justin Shi. Seeking the Principles of Sustainable Software
Engineering~\cite{wssspe2_shi}

\item Colin C. Venters, Michael K. Griffiths, Violeta Holmes, Rupert R. Ward, and
David J. Cooke. The Nebuchadnezzar Effect: Dreaming of Sustainable Software
through Sustainable Software Architectures~\cite{wssspe2_venters}
\end{itemize}

>>>>

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Exploring Sustainability group are:
\begin{itemize}
\item Mario Rosado de Souza, Robert Haines, and Caroline Jay. Defining
sustainability through developers' eyes: Recommendations from an interview
study~\cite{wssspe2_rosada_de_souza}

\item Robert Downs, W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and
Nicholas Weber. Community recommendations for sustainable scientific
software~\cite{wssspe2_downs}

\item Abani Patra, Matthew Jones, Steven Gallo, Kyle Marcus, and Tevfik Kosar.
Role of online platforms, communications and workflows in developing sustainable
software for science communities~\cite{wssspe2_patra}

\item Marlon Pierce, Suresh Marru, and Chris Mattmann. {WSSSPE2}: Patching it up,
pulling it forward~\cite{wssspe2_pierce}

\item Justin Shi. Seeking the principles of sustainable software
engineering~\cite{wssspe2_shi}

\item Colin C. Venters, Michael K. Griffiths, Violeta Holmes, Rupert R. Ward, and
David J. Cooke. The Nebuchadnezzar effect: dreaming of sustainable software
through sustainable software architectures~\cite{wssspe2_venters}
\end{itemize}
